Ch3 process

### 2022-02-17 Ch3_samplesize/Ch3_process.Rmd
Ah! running 1000

```{r results='hide'}
nreps <- 100
gp.mles.reps <- data.frame(NULL)

@@

>>>>

```{r results='hide'}
nreps <- 1000
gp.mles.reps <- data.frame(NULL)

@@

Restrict the y axis

gp.mles.reps %>% 
  mutate(tru.tails = rep(tru.cdfs$w.cdfs, n.tru.cdfs),
         tails.ratio = tail/tru.tails,
         thresh = factor(threshold),
         samp.size = factor(samp.size)) %>%
  drop_na(tails.ratio) %>% 
  mutate(nice.tails = signif(tails.ratio, 3)) %>% 
  ggplot(., aes(x = samp.size, y = tails.ratio, color = thresh)) +
  geom_boxplot() +
  labs(title = "Lomax") +
  lims(y = c(-1, 3)) +
  theme_minimal() -> lomax.tail

gp.mles.reps %>% 
  mutate(tru.tails = rep(tru.cdfs$w.cdfs, n.tru.cdfs),
         gp.tails.ratio = gp.tail/tru.tails,
         thresh = factor(threshold),
         samp.size = factor(samp.size)) %>%
  mutate(nice.tails = signif(gp.tails.ratio, 3)) %>% 
  ggplot(., aes(x = samp.size, y = gp.tails.ratio, color = thresh)) +
  geom_boxplot() +
  labs(title = "GP") +
  lims(y = c(-1, 3)) +
  theme_minimal() -> gp.tail

Check the mean:

```{r}
gp.mles.reps %>% 
  mutate(tru.tails = rep(tru.cdfs$w.cdfs, n.tru.cdfs),
         tails.ratio = tail/tru.tails,
         gp.tails.ratio = gp.tail/tru.tails) %>% 
  group_by(samp.size, threshold) %>% 
  summarise(mean.ratio = mean(tails.ratio),
            mean.gp.ratio = mean(gp.tails.ratio))
```
